### 2019-08-20 reports/thesis/chapters/3_compoundPoisson.tex
add graphical model figure
Use 1 sigma confidence interval

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\mainSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha1beta1.eps}
        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
    \end{subfigure}
    }
    \vspace{2em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha1beta1.eps}
        \caption{Q-Q plot}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method. In a), the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency or frequency density.}
    \label{fig:compoundPoisson_histogram_1_1_1}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\mainSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha100beta1.eps}
        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
    \end{subfigure}
    }
    \vspace{2em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha100beta1.eps}
        \caption{Q-Q plot}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method. In a), the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency or frequency density.}
    \label{fig:compoundPoisson_histogram_1_100_1}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha1beta1.eps}
        \caption{$\CPoisson(1,1,1)$ Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha1beta1.eps}
        \caption{$\CPoisson(1,1,1)$ saddlepoint approx.}
    \end{subfigure}
    }
    \vspace{1em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha100beta1.eps}
        \caption{$\CPoisson(1,100,1)$ Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha100beta1.eps}
        \caption{$\CPoisson(1,100,1)$ saddlepoint approx.}
        \label{fig:compoundPoisson_histogram_approx_1_100_1}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,\alpha,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using approximate methods. The dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_approx}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda10alpha1beta1.eps}
        \caption{Histogram - Exact method}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda10alpha1beta1.eps}
        \caption{Q-Q plot - Exact method}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda10alpha1beta1.eps}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda10alpha1beta1.eps}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda10alpha1beta1.eps}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda10alpha1beta1.eps}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(10,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f. On the left, the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_10_1_1}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda100alpha100beta1.eps}
        \caption{Histogram - Exact method}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda100alpha100beta1.eps}
        \caption{Q-Q plot - Exact method}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda100alpha100beta1.eps}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda100alpha100beta1.eps}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda100alpha100beta1.eps}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda100alpha100beta1.eps}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(100,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f. On the left, the dotted red line shows the $\Phi(+1)-\Phi(-1)$ confidence interval of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_100_1_1}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{../figures/compoundpoisson/graphicalModel.eps}
  \caption{Graphical model of the grey value $X_{i,j}$ for each of the $m$ pixels in the $n$ replicate projections. $Y_{i,j}\sim\poisson(\lambda_i)$ is the photon count. The grey value has a compound Poisson gamma element $X_{i,j}|Y_{i,j}\sim\gammaDist(Y_{i,j}\alpha,\beta)$ and can be extended by adding electronic noise $\epsilon_{i,j}\sim\normal(a,\kappa)$.}
  \label{fig:compoundPoisson_graphicalModel}
\end{figure}

>>>>

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\mainSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha1beta1.eps}
        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
    \end{subfigure}
    }
    \vspace{2em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha1beta1.eps}
        \caption{Q-Q plot}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method. In a), the dotted red line shows the 68\% confidence interval of the expected frequency or frequency density.}
    \label{fig:compoundPoisson_histogram_1_1_1}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\mainSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda1alpha100beta1.eps}
        \caption{Left: Observed and expected frequency of a zero. Right: Histogram and p.d.f.~of non-zero values.}
    \end{subfigure}
    }
    \vspace{2em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda1alpha100beta1.eps}
        \caption{Q-Q plot}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using the exact method. In a), the dotted red line shows the 68\% confidence interval of the expected frequency or frequency density.}
    \label{fig:compoundPoisson_histogram_1_100_1}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha1beta1.eps}
        \caption{$\CPoisson(1,1,1)$ Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha1beta1.eps}
        \caption{$\CPoisson(1,1,1)$ saddlepoint approx.}
    \end{subfigure}
    }
    \vspace{1em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha100beta1.eps}
        \caption{$\CPoisson(1,100,1)$ Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha100beta1.eps}
        \caption{$\CPoisson(1,100,1)$ saddlepoint approx.}
        \label{fig:compoundPoisson_histogram_approx_1_100_1}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,\alpha,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using approximate methods. The dotted red line shows the 68\% confidence interval of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_approx}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda10alpha1beta1.eps}
        \caption{Histogram - Exact method}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda10alpha1beta1.eps}
        \caption{Q-Q plot - Exact method}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda10alpha1beta1.eps}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda10alpha1beta1.eps}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda10alpha1beta1.eps}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda10alpha1beta1.eps}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(10,1,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f. On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_10_1_1}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonlambda100alpha100beta1.eps}
        \caption{Histogram - Exact method}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonlambda100alpha100beta1.eps}
        \caption{Q-Q plot - Exact method}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda100alpha100beta1.eps}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda100alpha100beta1.eps}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda100alpha100beta1.eps}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda100alpha100beta1.eps}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(100,100,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f. On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_100_1_1}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{../figures/compoundpoisson/graphicalModel.pdf}
  \caption{Graphical model of the grey value $X_{i,j}$ for each of the $m$ pixels in the $n$ replicate projections. $Y_{i,j}\sim\poisson(\lambda_i)$ is the photon count. The grey value has a compound Poisson gamma element $X_{i,j}|Y_{i,j}\sim\gammaDist(Y_{i,j}\alpha,\beta)$ and can be extended by adding electronic noise $\epsilon_{i,j}\sim\normal(a,\kappa)$.}
  \label{fig:compoundPoisson_graphicalModel}
\end{figure}

### 2019-08-20 reports/thesis/chapters/4_variancePrediction.tex
Use 1 sigma confidence interval

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg30_identity000010.eps}
        \caption{${y}(x)=\beta_0+\beta_1 x$ at \ang{30}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg30_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{30}}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_identity000010.eps}
        \caption{${y}(x)=\beta_0+\beta_1 x$ at \ang{120}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{120}}
    \end{subfigure}
    }
    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilter} with linear shading correction. The solid red line shows the GLM fit along with the 95\% prediction interval as dashed lines.}
    \label{fig:meanVar_varMeanExample_AbsNoFilter}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg30_identity000100.eps}
        \caption{${y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{30}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg30_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{30}}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_identity000100.eps}
        \caption{${y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{120}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{120}}
    \end{subfigure}
    }
    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilter} with linear shading correction. The solid red line shows the GLM fit along with the 95\% prediction interval as dashed lines.}
    \label{fig:meanVar_varMeanExample_AbsFilter}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsNoFilterDeg30_vsgreyvalue.eps}
      \caption{\texttt{AbsNoFilter} at \ang{30}}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsNoFilterDeg120_vsgreyvalue.eps}
      \caption{\texttt{AbsFilter} at \ang{120}}
  \end{subfigure}
  }
  \centerline{
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsFilterDeg30_vsgreyvalue.eps}
      \caption{\texttt{AbsFilter} at \ang{30}}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsFilterDeg120_vsgreyvalue.eps}
      \caption{\texttt{AbsFilter} at \ang{120}}
  \end{subfigure}
  }
  \caption{Log frequency density histogram of the residuals given the mean grey value. The residuals are from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections. The dashed red line shows the 95\% confidence interval of the predicted residual.}
  \label{fig:meanVar_residualGreyvalue}
\end{figure}

>>>>

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg30_identity000010.eps}
        \caption{${y}(x)=\beta_0+\beta_1 x$ at \ang{30}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg30_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{30}}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_identity000010.eps}
        \caption{${y}(x)=\beta_0+\beta_1 x$ at \ang{120}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsNoFilterDeg120_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}\beta_0)^{-1}$ at \ang{120}}
    \end{subfigure}
    }
    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsNoFilter} with linear shading correction. The solid red line shows the GLM fit along with the 68\% prediction interval as dashed lines.}
    \label{fig:meanVar_varMeanExample_AbsNoFilter}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg30_identity000100.eps}
        \caption{${y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{30}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg30_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{30}}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_identity000100.eps}
        \caption{${y}(x)=\beta_{-1}x^{-1}+\beta_0$ at \ang{120}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/varmean/varMeanExample_AbsFilterDeg120_reciprocal000100.eps}
        \caption{${y}(x)=(\beta_{-1}x^{-1}+\beta_0)^{-1}$ at \ang{120}}
    \end{subfigure}
    }
    \caption{Log frequency density histogram of the sample variance-mean data from \texttt{AbsFilter} with linear shading correction. The solid red line shows the GLM fit along with the 68\% prediction interval as dashed lines.}
    \label{fig:meanVar_varMeanExample_AbsFilter}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsNoFilterDeg30_vsgreyvalue.eps}
      \caption{\texttt{AbsNoFilter} at \ang{30}}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsNoFilterDeg120_vsgreyvalue.eps}
      \caption{\texttt{AbsFilter} at \ang{120}}
  \end{subfigure}
  }
  \centerline{
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsFilterDeg30_vsgreyvalue.eps}
      \caption{\texttt{AbsFilter} at \ang{30}}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/varmean/varMeanResidualAbsFilterDeg120_vsgreyvalue.eps}
      \caption{\texttt{AbsFilter} at \ang{120}}
  \end{subfigure}
  }
  \caption{Log frequency density histogram of the residuals given the mean grey value. The residuals are from fitting a gamma GLM of the form ${y}(x)=\beta_0+\beta_1 x$ onto the sample variance-mean data obtained from the replicated projections. The dashed red line shows the 68\% confidence interval of the predicted residual.}
  \label{fig:meanVar_residualGreyvalue}
\end{figure}
